---
title: "Course Project: Calories and BMI Calculator"
author: "Roberto Rojas"
date: "October 31, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Course Project

- This is the final course project for Data Products Course
- The objective is to create a shiny application

## Calculator

- Takes in the input as amount of fats, protein and carbs taken (in grams)
- Based on the above information the application calculates the Calories using following formulae:
- Calories = 9 * (gms of fats) + 4 * (gms of protein) + 4 * (gms of carbs)
- BMI = weight (kgr) / height^2 (meters)


## R code embedded in the slide

- Input defined are amount of fats, protein and carbs taken (in grams)
- Calculation of Calories and BMI

```{r echo=TRUE}
protien_gms <- 10
fat_gms <- 10
carbs_gms <- 10
total_calories <- fat_gms * 9.0 + protien_gms * 4.0 + carbs_gms * 4.0
total_calories
```

## R code BMI calculation

```{r echo=TRUE}
weight<-88
height<-1.77
bmi<- weight/(height^2)
bmi
```

## The Shiny Application

- The source code can be found at:
https://github.com/RobFX14/Project-Shiny

- Presentation:
https://robfx14.shinyapps.io/ShinyProject/
